Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-02 manuscript/manuscript.Rmd
singular/plural consistency for citations

Outside of telematics, @yang_2018 uses a gradient tree-boosting approach to 
capture non-linearities that would be a challenge for GLMs. @henckaerts_2018 
makes use of generalized additive models (GAM) to improve predictions of GLMs.
Many researchers, in an apparent effort to demonstrate the range of possibilities
and advantages of machine learning, have approached the topic by comparing many
different machine learning algorithms within a single study, such as in
@dugas_2003, @noll_2018, @spedicato_2018. These studies make use of such varied
techniques as regression trees, boosting machines, support vector machines, and 
neural networks.

@@

It is interesting to note that the modelers, who are most familiar with the
models, tend to be same people designing and communicating the explanations.
This poses a challenge that @millerExplainableAI2017 calls "inmates running
the asylum", where the modelers design explanations for *themselves* rather
than the intended audience. For example, they may be interested in technical
questions, such as extrapolation behavior, and shape the explanations accordingly,
which may be irrelevant to a prospective policyholder.

>>>>

Outside of telematics, @yang_2018 use a gradient tree-boosting approach to 
capture non-linearities that would be a challenge for GLMs. @henckaerts_2018 
make use of generalized additive models (GAM) to improve predictions of GLMs.
Many researchers, in an apparent effort to demonstrate the range of possibilities
and advantages of machine learning, have approached the topic by comparing many
different machine learning algorithms within a single study, such as in
@dugas_2003, @noll_2018, @spedicato_2018. These studies make use of such varied
techniques as regression trees, boosting machines, support vector machines, and 
neural networks.

@@

It is interesting to note that the modelers, who are most familiar with the
models, tend to be same people designing and communicating the explanations.
This poses a challenge that @millerExplainableAI2017 call "inmates running
the asylum", where the modelers design explanations for *themselves* rather
than the intended audience. For example, they may be interested in technical
questions, such as extrapolation behavior, and shape the explanations accordingly,
which may be irrelevant to a prospective policyholder.
